Analysis-ready VCF at Biobank-scale using Zarr

### 2024-05-08 diagrams/data-model.tex

%% compresion
 \node (numcodecs) [rectangle, draw, densely dotted, thick, rounded corners, minimum width=2.4cm, minimum height=2.6cm, anchor= south west]
    at (4.8,2.2) {};
 \node[anchor=north,below] at (numcodecs.north) {\scriptsize Filter \& compress};
 %\node[anchor=south,below] at (numcodecs.south) {numcodecs};
 \node (blosk) [rectangle, ultra thick, red, draw, rounded corners, minimum width=1.8cm, minimum height=1.6cm, anchor=center,align=center,text=black]
    at (numcodecs) {\scriptsize Blosc\\\scriptsize ZSTD\\\scriptsize BITSHUFFLE};
 \draw[ultra thick, red,-stealth] (3.9,3.5,-.25) -- (5,3.5,-.25);

>>>>

%% compresion
 \node (numcodecs) [rectangle, draw, densely dotted, thick, rounded corners, minimum width=2.4cm, minimum height=2.6cm, anchor= south west]
    at (4.8,2.2) {};
 \node[anchor=north,below] at (numcodecs.north) {\scriptsize Filter \& compress};
 %\node[anchor=south,below] at (numcodecs.south) {numcodecs};
 \node (blosk) [rectangle, ultra thick, red, draw, rounded corners, minimum width=1.8cm, minimum height=1.6cm, anchor=center,align=center,text=black]
    at (numcodecs) {\scriptsize Blosc\\\scriptsize Zstandard\\\scriptsize BitShuffle};
 \draw[ultra thick, red,-stealth] (3.9,3.5,-.25) -- (5,3.5,-.25);
